---
output:
  pdf_document: default
  html_document: default
---
Prosper Loan Data Exploratory Data Analysis by Véber István
========================================================

This analysis explores the prosper dataset. According to there website: 
"Through Prosper, people can invest in each other in a way that is financially 
and socially rewarding. Borrowers apply online for a fixed-rate, fixed-term loan
between $2,000 and $40,000. Individuals and institutions can invest in loans
and earn attractive returns. Prosper handles all loan servicing on behalf of the
matched borrowers and investors."

In the original dataset there are 81 variables, during the analysis the
following variables were retained:
source:
https://rstudio-pubs-static.s3.amazonaws.com/86324_ab1e2e2fa210452f80a1c6a1476d7a2a.html

Term:	The length of the loan expressed in months.
LoanStatus:	The current status of the loan: Cancelled, Chargedoff, Completed, 
  Current, Defaulted, FinalPaymentInProgress, PastDue.
BorrowerRate:	The Borrower's interest rate for this loan.
EstimatedReturn:	The estimated return assigned to the listing at the time it 
  was created. 
ProsperRating:	The Prosper Rating assigned at the time the listing was created:
  0 - N/A, 1 - HR, 2 - E, 3 - D, 4 - C, 5 - B, 6 - A, 7 - AA. 
ProsperScore:	A custom risk score built using historical Prosper data. The score
  ranges from 1-10, with 10 being the best, or lowest risk score. 
ListingCategory:	The category of the listing that the borrower selected when 
  posting their listing.
BorrowerState:	The two letter abbreviation of the state of the address.
EmploymentStatus:	The employment status of the borrower.
EmploymentStatusDuration:	The length in months of the employment status.
IsBorrowerHomeowner	Borrower is homeowner or not.
DebtToIncomeRatio:	The debt to income ratio of the borrower at the time the 
  credit profile was pulled. This value is Null if the debt to income ratio is 
  not available. This value is capped at 10.01.
IncomeRange:	The income range of the borrower.
IncomeVerifiable:	The borrower indicated they have the required documentation to
  support their income.
StatedMonthlyIncome:	The monthly income the borrower stated.
LoanOriginalAmount:	The origination amount of the loan.
LoanOriginationDate:	The date the loan was originated.
MonthlyLoanPayment:	The scheduled monthly loan payment.

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(knitr)
library(dplyr)
library(gridExtra)
library(ggthemes)
library(scales)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
df_full <- read.csv('prosperLoanData.csv')
```

```{r echo=FALSE}
# select variables
df = select(df_full, 
                Term,
                LoanStatus,
                BorrowerRate,
                EstimatedReturn,
                ProsperRating..numeric.,
                ProsperScore,
                ListingCategory..numeric.,
                BorrowerState,
                EmploymentStatus,
                EmploymentStatusDuration,
                IsBorrowerHomeowner,
                DebtToIncomeRatio,
                IncomeRange,
                IncomeVerifiable,
                StatedMonthlyIncome,
                LoanOriginalAmount,
                LoanOriginationDate,
                ListingCreationDate,
                LoanOriginationQuarter,
                MonthlyLoanPayment
)
names(df)[names(df)=="ProsperRating..numeric."] <- "ProsperRating"
names(df)[names(df)=="ListingCategory..numeric."] <- "ListingCategory"
dim(df)
```
```{r echo=FALSE}
# ListingCategory is numeric in the dataset, convert to strings
df$ListingCategory <- factor(df$ListingCategory,
                                labels = c("Not Available","Debt Consolidation","Home Improvement","Business",
                                           "Personal Loan","Student Use","Auto","Other","Baby&Adoption","Boat",
                                           "Cosmetic Procedures","Engagement Ring","Green Loans","Household Expenses",
                                           "Large Purchases","Medical/Dental","Motorcycle","RV","Taxes","Vacation","Wedding Loans"))

# make scores and ratings oredered
df$ProsperRating <- factor(df$ProsperRating, levels = c("NA", "1", "2", "3", "4", "5", "6", "7"), ordered = TRUE)
df$ProsperScore <- factor(df$ProsperScore, levels = c("NA", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11"), ordered = TRUE)

# convert to date
df$LoanOriginationDate <- as.Date(df$LoanOriginationDate)
df$ListingCreationDate <- as.Date(df$ListingCreationDate)

df$Term <- factor(df$Term)

str(df)
```

19 variables are retained for exploration.

```{r echo=FALSE}
# find nan in columns
apply(is.na(df), 2, sum)
```

```{r echo=FALSE}
ggplot(aes(x = ListingCreationDate, y = ProsperRating), data = df) + geom_line()
```

Some variables have no data prior 2009-07-13, these dates were dropped.

```{r echo=FALSE}
# drop early dates
df <- subset(df, ListingCreationDate >= '2009-07-13')
apply(is.na(df), 2, sum)
```

After dropping early dates only the DebtToIncomeRatio variable has in our 
dataset a large number of nan rows (7296). This is because the isn't verifiable,
and this alone can be an interesting group to examine, so these rows are 
retained.

```{r}
df$LoanStatus <- as.character(df$LoanStatu)
df$LoanStatus[df$LoanStatus == 'Defaulted'] <- 'Failed'
df$LoanStatus[df$LoanStatus == 'Chargedoff'] <- 'Failed'
df$LoanStatus[df$LoanStatus == 'Cancelled'] <- 'Failed'
df$LoanStatus[df$LoanStatus == 'FinalPaymentInProgress'] <- 'Completed'
df$LoanStatus[df$LoanStatus == 'Past Due (>120 days)'] <- 'Past'
df$LoanStatus[df$LoanStatus == 'Past Due (1-15 days)'] <- 'Past'
df$LoanStatus[df$LoanStatus == 'Past Due (16-30 days)'] <- 'Past'
df$LoanStatus[df$LoanStatus == 'Past Due (31-60 days)'] <- 'Past'
df$LoanStatus[df$LoanStatus == 'Past Due (61-90 days)'] <- 'Past'
df$LoanStatus[df$LoanStatus == 'Past Due (91-120 days)'] <- 'Past'
df$LoanStatus <- as.factor(df$LoanStatus)
levels(df$LoanStatus)
```

The LoanStatus variable has too many levels to explore, they are regrouped to 
the following 4 groups: "Completed", "Current", "Failed", "Past"

# Univariate Plots Section

```{r echo=FALSE, Univariate_Plots}
plot1 <-  ggplot(aes(x = LoanOriginalAmount), data = df) + 
          geom_histogram(binwidth = 100)
plot2 <-  ggplot(aes(x = LoanOriginalAmount), data = df) + 
          geom_histogram(binwidth = 2000)
grid.arrange(plot1, plot2, ncol=2)
summary(df$LoanOriginalAmount)
```

According to the site, the loan range is between $2,000 and $40,000, but in the 
dataset the minimum amount is $1,000. When the dataset was made the loan range 
was different.

A large proportion of the loans are under $15,000. Some round numbers are very
popular: $400, $10,000, $15,000, the median loan is $7,500.

```{r echo=FALSE}
ggplot(df, aes(x=ListingCategory, (y=..count../sum(..count..)))) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
summary(df$ListingCategory)
```

The most popular choice is debt consolidation by far, other popular reasons are home improvement, business, and auto.

```{r echo=FALSE}
ggplot(aes(x = LoanOriginationDate), data = df) + 
          geom_histogram(binwidth = 30) +
          geom_histogram(binwidth = 7, color="CadetBlue") +
          geom_histogram(binwidth = 1, color="coral")
summary(df$LoanOriginationDate)
```

During the period the number of new loans is growing, but at the and of 2012 
was a fallback, and only in the middle of 2013 reached the number of new loans 
the earlier record. In the chart, the grey columns are the number of new loans in
a 30 days period. The blue columns are the new loans per week, and the orange 
the loans per day.  

```{r echo=FALSE}
plot1 <- ggplot(df, aes(x=LoanStatus, y=..count../sum(..count..))) + geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
plot2 <- ggplot(subset(df, df$LoanStatus == "Completed" | df$LoanStatus == "Failed"), aes(x=LoanStatus, y=..count../sum(..count..))) + geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
grid.arrange(plot1, plot2, ncol=2)
```

At the time of the last date in the dataset almost 70% of the loans were in the 
"Current" group, this signs the rapid growth of the loan numbers. If we focus 
on the completed or failed loans we can see that a quarter of the loans failed 
(defaulted or charged-off).

```{r echo=FALSE, warning=FALSE}
ggplot(df) + 
  geom_histogram(aes(x = BorrowerRate, color = "BorrowerRate"), alpha=0.6,binwidth=0.01,position="dodge", size=1) +
                      scale_x_continuous(breaks=seq(-0.1,0.35,0.1), limits=c(-0.1,0.35)) +
  geom_histogram(aes(x = EstimatedReturn, color = "EstimatedReturn"), alpha=0.6,binwidth=0.01,position="dodge", size=1) + 
  xlab("BorrowerRate or EstimatedReturn")
summary(df$BorrowerRate)
summary(df$EstimatedReturn)
```

EstimatedReturn is the difference between the Estimated Effective Yield and the 
Estimated Loss Rate. EstimatedReturn has a nice bell shaped distribution, while 
BorrowerRate is a bit bimodal. The range of BorrowerRate is larger. 
EstimatedReturn some cases can be negative.

```{r echo=FALSE}
ggplot(df, aes(x=BorrowerState)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Prosper is really popular in California, most of the borrowers are from that 
state.

```{r echo=FALSE}
ggplot(df) + 
  geom_area(aes(x = MonthlyLoanPayment), binwidth=10, stat = "bin", color = "black", fill = "CadetBlue") +
  scale_x_continuous(breaks=seq(0,2200,100)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
summary(df$MonthlyLoanPayment)

# source: https://stackoverflow.com/questions/2547402/is-there-a-built-in-function-for-finding-the-mode
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
mode <- Mode(df$MonthlyLoanPayment)
paste("Mode: ", mode)
```

Some people pay more than $2,000 a month, but the median monthly pay is only 
$251.9, and there is a high peak between $150 and $200. This distribution has a 
long right tail.

```{r echo=FALSE, warning=FALSE}
ggplot(df) + 
  geom_area(aes(x = DebtToIncomeRatio), binwidth=0.05, stat = "bin", color = "black", fill = "CadetBlue") +
  scale_x_log10() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
summary(df$DebtToIncomeRatio)
```

The DebtToIncomeRatio is maximized at 10.01. The median is 0.259, and the third 
quartile is 0.320, so only a few people have DebtToIncomeRatio larger than 1.0. 
With a log10 transformation, we have a nice bell shape.

```{r echo=FALSE, warning=FALSE}
ggplot(df) + 
  geom_area(aes(x = StatedMonthlyIncome), binwidth=0.02, stat = "bin", color = "black", fill = "CadetBlue") +
  scale_x_log10() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  coord_cartesian(xlim=c(100, 100000))
summary(df$StatedMonthlyIncome)
```

The median StatedMonthlyIncome is exactly $5000. This is the income stated by 
the borrower. Most likely these states are only estimates. Half of the people 
have StatedMonthlyIncome between $3,434 and $7,083.

```{r echo=FALSE}
ggplot(df, aes(x=ListingCategory, y=LoanOriginalAmount)) + 
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

The loans with the largest median are for debt consolidation, baby & adoption, 
wedding, and business. Student loans are the smallest ones.


# Univariate Analysis

### What is the structure of your dataset?

The original dataset has 81 variables and 113937 observations. Because this 
dataset was very large and difficult to traverse a subset was used, where 20 
variables were retained. The loans before 2009-07-13 were dropped because of a 
lot of missing data.

### What is/are the main feature(s) of interest in your dataset?

My main interest is to find the characteristics of "bad" loans. I simplified 
the LoanStatus variable. There were too many similar levels. They are regrouped 
to the following 4 groups: "Completed", "Current", "Failed", "Past".

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

                Term,
                BorrowerRate,
                EstimatedReturn,
                ProsperRating,
                ProsperScore,
                ListingCategory,
                BorrowerState,
                DebtToIncomeRatio,
                IncomeRange,
                StatedMonthlyIncome,
                LoanOriginalAmount,
                LoanOriginationDate,
                MonthlyLoanPayment

### Did you create any new variables from existing variables in the dataset?

I regrouped, refactored the LoanStatus with new levels.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

A large portion of the loans are round numbers, very popular amounts are: $400, 
$10,000, $15,000.
Far the most popular cause of borrowing loan is debt consolidation.
At the and of 2012 the number of new loans dropped for some months.
In some rear cases, the Estimated return can be negative.
The service is most popular in California.
The is a high peak in the MonthlyLoanPayment distribution between $150 and $200.
DebToIncome ratio above 1.0 is rare. With a log10 transformation, we get a nice 
bell-shaped distribution. StatedMonthlyIncome with log10 transformation results 
in a bell shape as well.
For debt consolidation or baby & adoption the median loans are relatively high, 
but for student use small.



# Bivariate Plots Section

```{r echo=FALSE, Bivariate_Plots}
ggplot(df, aes(x=LoanOriginalAmount)) + 
  geom_histogram(binwidth = 0.1) + 
  scale_x_log10() +
  facet_wrap(~LoanStatus, scales="free") +
  coord_cartesian(xlim=c(1000, 100000))
```

The distribution of LoanOriginalAmount in case of failed and completed loans 
doesn't show a salient difference, but the proportion of current loans larger 
than $10,000 is relatively large.

```{r echo=FALSE}
ggplot(df, aes(x=BorrowerRate)) + 
  geom_histogram(binwidth = 0.02) + 
  facet_wrap(~LoanStatus, scales="free")
```

The distribution of BorrowerRate in case of completed loans can be considered 
uniform, current loans are right-skewed. But failed and past due loans are 
left-skewed. Probably higher BorrotRates are assigned to more risky borrowers.

```{r echo=FALSE}
ggplot(df) + 
  geom_bar(aes(x=ProsperRating)) + 
  facet_wrap(~LoanStatus, scales="free")
```

Higher ProsperRating is better. This shows how risky the borrower is. This 
distributions are similar to the distributions of Borrowerate, but mirrored.
Failed loans have a large proportion of bad ProsperRatings.

```{r echo=FALSE}
ggplot(df, aes(x = ProsperRating, y = BorrowerRate)) +
  geom_point(alpha= 0.2, position = position_jitter(h=0))
```

From the earlier distribution we could anticipate some negative correlation
between ProsperRating and BorrowerRate. Here we can clearly see that the largest
the ProsperRating the smallest the BorrowerRate.

```{r echo=FALSE}
ggplot(df, aes(x = LoanOriginationDate, fill = LoanStatus)) +
  geom_bar(stat = "bin", binwidth=30, color = "grey40")
```

This plot shows the count of LoanStatus levels during the period. The oldest 
Current loans were opened in the first half of 2011. 

```{r echo=FALSE}
# proportional stacked bars code source: https://afit-r.github.io/barcharts
# calculate percentages
proportion <- subset(df, df$LoanStatus != "Current") %>%
        group_by(ListingCategory, LoanStatus) %>%
        tally() %>%
        group_by(ListingCategory) %>%
        mutate(pct = n / sum(n))

# create proportional stacked bars
ggplot(proportion, aes(ListingCategory, pct, fill = LoanStatus)) +
        geom_bar(stat = "identity", color = "grey40") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

In the above plot, the current loans are omitted. Past Due loans can be 
completed later, and later can become Current, but I wanted to see the 
"problematic" loans, so I only omitted the Current loans. Very interesting that 
the Green Loans perform so badly. Medical/Dental loans have a large portion of 
Past Due or Failed loans as well. But students are really reliable.

```{r echo=FALSE}
# calculate percentages
proportion <- subset(df, df$LoanStatus != "Current") %>%
        group_by(EmploymentStatus, LoanStatus) %>%
        tally() %>%
        group_by(EmploymentStatus) %>%
        mutate(pct = n / sum(n))

# create proportional stacked bars
ggplot(proportion, aes(EmploymentStatus, pct, fill = LoanStatus)) +
        geom_bar(stat = "identity", color = "grey40") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Current loans are omitted here as well. This plot shows, what most of us would 
anticipate, employed borrowers, perform better, not employed and other groups 
perform worst.


# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

Loans with lower ProsperRating are more probable to fail. It is interesting that 
Green Loans has so large proportion of Failed or Past Due loans, and Student Use 
performs so well. And as we would anticipate employed people are better at 
paying back loans. 

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

ProsperRating and BorrowerRate have a strong negative linear association, the 
lower the ProsperRating the higher the BorrowerRate.

### What was the strongest relationship you found?

ProsperRating vs BorrowerRate


# Multivariate Plots Section

```{r echo=FALSE, warning=FALSE}
ggplot(subset(df, df$LoanStatus != "Current"), aes(LoanOriginalAmount, StatedMonthlyIncome, colour = LoanStatus)) +
  geom_point(alpha= 0.4, position = position_jitter()) +
  scale_y_log10() + 
  scale_x_log10() + 
  coord_cartesian(ylim=c(1000, 50000)) +
  geom_smooth(size=1, alpha=1, level=0) +
  scale_color_brewer(type='qual', palette = "Set1")
```

LoanOriginalAmount tends to be higher with StatedMonthlyIncome. With the same LoanOriginalAmount to the Completed loans belongs higher mean 
StatedMonthlyIncome than to the Failed loans, regardless of the loan size.

```{r echo=FALSE, warning=FALSE}
ggplot(df, aes(LoanOriginalAmount, DebtToIncomeRatio, colour = ProsperRating)) +
  geom_point(alpha= 0.3, size=1, position = position_jitter()) +
  geom_smooth(size=1, alpha=1, level=0) +
  scale_y_log10() +
  scale_x_log10() +
  coord_cartesian(xlim=c(1000, 35000), ylim = c(0.05, 1.0)) +
  facet_wrap(~LoanStatus) + 
  scale_color_brewer(type='div') +
  theme(panel.background = element_rect(fill = 'black'))
```

As the LoanOriginalAmount tends to be higher the DebtToIncomeRate tends to be 
higher as well in most cases, but there are some exceptions. In the case of 
Current loans the mean DebtToIncomeRate decreases with the largest 
LoanOriginalAmounts. In the Failed plot in the case of the best ProsperRatings 
(6,7) the DebtToIncomeRate tends to decrease when the LoanOriginalAmounts 
increases. To better ProsperRating belongs lower DebtToIncomeRating.

```{r echo=FALSE}
ggplot(df, aes(LoanOriginalAmount, MonthlyLoanPayment, colour = Term)) +
  geom_point(alpha= 0.2, position = position_jitter(h=0)) +
  geom_smooth(size=1, alpha=1, level=0)
```

LoanOriginalAmount and MonthlyLoanPayment have a strong linear relationship and 
the steepness of this relationship is determined by the Term length.


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

LoanOriginalAmount tends to be higher with StatedMonthlyIncome. With the same 
LoanOriginalAmount to the Completed loans belongs higher mean 
StatedMonthlyIncome than to the Failed loans, regardless of the loan size.

As the DebtToIncomeRatio tends to be higher the ProsperRating tends to be worse 
(lower).

LoanOriginalAmount and MonthlyLoanPayment have a strong linear relationship and 
the steepness of this relationship is determined by the Term length.

### Were there any interesting or surprising interactions between features?

In the case of Failed loans the association between LoanOriginalAmount and 
DebtToIncomeRatio is strange. With most ProsperRatings as the LoanOriginalAmount 
tends to increase the DebtToIncomeRatio tends to increase as well. In the case 
of the best ProsperRating the association seems to be the opposite.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(df, aes(x=ListingCategory, y=LoanOriginalAmount)) + 
  geom_boxplot(aes(fill = ListingCategory)) +
  stat_summary(fun.y = mean, geom = "point", shape = 3, size = 3) +
  theme_minimal() +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Boxplot of the loan amounts by purpose of the loan") +
  theme(plot.title = element_text(size = 18, face = "bold"), axis.title = element_text(face="bold")) +
  xlab("Purpose of the loan") + 
  ylab("Loan Amount") +
  coord_cartesian(ylim = c(0,20000))
```

### Description One
In this plot, we can see why the borrowers apply for a loan and how much amount 
they borrow for different purposes. Besides the median, we can see the mean as 
well (+ sign). The highest median and average amount belong to Debt 
Consolidation, Baby&Adoption, Business, and Wedding. The smallest amounts are 
borrowed for Student Use.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(df, aes(x=ProsperRating, fill = ProsperRating)) + 
        geom_bar(color = "grey40") + 
        scale_fill_brewer(palette="OrRd") +
        facet_wrap(~LoanStatus, scales="free") +
        theme_minimal() +
        ggtitle("Number of loans by prosper rating in loan status groups") +
        theme(plot.title = element_text(size = 14, face = "bold"), axis.title = element_text(face="bold")) +
        xlab("Prosper Rating") + 
        ylab("count")
```

### Description Two
In this plot, we can see that the ProspeRating score works, because in the Failed 
level most loans belong to the worst ProsperRatings. 

### Plot Three
```{r echo=FALSE, Plot_Three}
# calculate percentages
proportion <- subset(df, df$LoanStatus != "Current") %>%
        group_by(EmploymentStatus, LoanStatus) %>%
        tally() %>%
        group_by(EmploymentStatus) %>%
        mutate(pct = n / sum(n))

# create proportional stacked bars
ggplot(proportion, aes(EmploymentStatus, pct, fill = LoanStatus)) +
        geom_bar(stat = "identity", color = "grey40") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("The percentage of good and bad loans without current loans") +
        theme(plot.title = element_text(size = 14, face = "bold"), axis.title = element_text(face="bold")) +
        xlab("Employment Status") + 
        ylab("percentage") +
        scale_fill_manual(values=c("#eddfc7", "#dac7ed", "#c7d4ed"))
```

### Description Three

There isn't any surprise in this plot. The largest proportion of Failed loans 
belong to the Not Employed and Other group. Full-time and Part-time employees 
are the most reliable.

------

# Reflection

Without deep domain knowledge, this was a difficult task to analyze the prosper 
dataset. It is hard to use 81 features. It was even a considerable time to 
filter the variables to analyze. During this process, I googled a lot of 
features to understand them.

I chose this dataset, because I thought it to be a challenging one, and in that 
I was right. First I wanted only to choose the most interesting variables, but 
without concept, there were too many interesting combinations.  It was easier to 
narrow the features when I decided that I want to focus on the "Failed" loans.

Finally, 20 features remained, but the combination with this number of features 
is really large as well.

This EDA was super for learning purpose. Before the course, I didn't use R, and
here I learned a lot about ggplot. Sometimes a struggled with the plots because 
they didn't want become the charts I wanted, but finally we agreed.

There are a large number of ways to take this project further, but a good next 
step could be a logistic regression with failed and finished loans.


